---
title: "Reformatting"
author: "Olaf"
date: "2/13/2019"
output: html_document
---

```{r}

```

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(tidyr)

# toi call stats filter 
```
```{r}
catch_original <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/df35b.302.1", method = "libcurl"),
                    stringsAsFactors = FALSE)
head(catch_original)

```

remove the all and notesRgCode columns using select Pipe operator is control shift M 

```{r}
catch_long <- catch_original %>% 
  select(-All, -notesRegCode) %>% 
  gather(key = "species", value = "catch", -Region, -Year)

head(catch_long)
```

```{r}
catch_wide <- catch_long %>% 
  spread(key = Region, value = catch)

head(catch_wide)
```

Mike Byerly. Alaska commercial salmon catches by management region (1886- 1997). Gulf of Alaska Data Portal. df35b.304.2.

# Clean up our data 

* Rename cathc to catch thousands
* Create a new number of fish 

```{r}
catch_clean <- catch_long %>% 
  rename(catch_thousands = catch) %>% 
  mutate(catch_thousands = ifelse(catch_thousands == "I", 1, catch_thousands)) %>% 
  mutate(catch_thousands = as.numeric(catch_thousands)) %>% 
  mutate(catch = catch_thousands * 1000) %>% 
  select(-catch_thousands)

head(catch_clean)
```

Look for where as numeric failed 


```{r}
test <- as.numeric(catch_long$catch)
i <- which(is.na(test) == TRUE)
catch_long[i,]
```


# Split - Apply - Combine

*calculate mean catch by species 

```{r}
species_mean <- catch_clean %>% 
  group_by(Year, species) %>% 
  summarise(catch_mean = mean(catch)) %>% 
  arrange(-Year, desc(species)) %>% 
  filter(Year >= 1990)
head(species_mean)
```


# Reformat Catch Data 

* remove "all column"
* create species column 
  -move from wide to long 
* general QA
# Join the Region Definitions 

# Misc 

*